Stable Hot Spot Analysis (Draft)

### 2017-06-16 paper-main.tex
Updated Appendix

Aggregation size 1 means we aggregate every point, which was in range of $100x100 \cdot 0.000001$ into one pixel. 
For aggregation size Z we aggregated ZxZ pixel from aggregated size 1 into a new pixel.
%
For our measurements we specified the following data series:
\begin{itemize}
 \item $W_i$: The weight matrix W is from 3 to 47 with a stepsize of 4.
 \item $F_j$: The focal matrix F is from  17 to 137 with a stepsize of 12. F is ignored for $G^*$ but not for Focal $G^*$
 \item $R_z$: The aggregation level is from 1 to 6 with a stepsize of 1. R represents the raster
\end{itemize}
\begin{definition}
The SoH for a singled evalution run in the weight dimension is defined as:
\begin{displaymath}
\SOHUP( G^*(R_z, W_i, st, F_{j}), G^*(R_z, W_{i+2}, st, F_{j}) ) 
\end{displaymath}
\begin{displaymath}
\SOHDOWN( G^*(R_z, W_i, st, F_{j}), G^*(R_z, W_{i+2}, st, F_{j}) )
\end{displaymath}
\begin{displaymath}
z \in [1,6], i,j \in [1,11], G^* \in [Standard, Focal]
\end{displaymath}
The SoH for a singled evalution run in the focal dimension is defined as:
\begin{displaymath}
\SOHUP( G^*(R_z, W_i, st, F_{j}), G^*(R_z, W_{i}, st, F_{j+1}) )
\end{displaymath}
\begin{displaymath}
\SOHDOWN( G^*(R_z, W_i, st, F_{j}), G^*(R_z, W_{i}, st, F_{j+1}) )
\end{displaymath}
\begin{displaymath}
z \in [1,6], i,j \in [1,11], G^* \in [Standard, Focal]
\end{displaymath}
The SoH for a singled evalution run in the aggregation dimension is defined as:
\begin{displaymath}
\SOHUP( G^*(R_z, W_i, st, F_{j}), G^*(R_{z+1}, W_{i}, st, F_{j}) )
\end{displaymath}
\begin{displaymath}
\SOHDOWN( G^*(R_z, W_i, st, F_{j}), G^*(R_{z+1}, W_{i}, st, F_{j}) )
\end{displaymath}
\begin{displaymath}
z \in [1,6], i,j \in [1,11], G^* \in [Standard, Focal]
\end{displaymath}

@@

\subsection{Clumping}
The SoH needs a parent and a child. Clusters can be calculated different. For $G^*$ a sigmoid can be used. Values above 2.58 and under -2.58 means in less then 
1\% of the cases you are wrong. The values of Focal $G^*$ depend on the focal size F. Therefore, we decide all values in the top quantile belong to a clusters.
For clustering we grouped the neighbourhood with values in the top quantile to one cluster. 
Neigbours are defined if they can be reached with a stepsize of 1 in x and y direction, independent of each other.
Which can be expressed in R with clumping, TODO which package and parametrisations.
In Fig.~\ref{fig:Clumping} we visualized the clusters. The clusters are marked in different colours yellow (child) and violet (parent).
It can seen that the results from $G^*$ and Focal $G^*$ differ. Focal $G^*$ has more smaller clusters which are distributed over the complete raster.
Not overlapping clusters should be not stable because if we changed the parametrisation we want that the clusters do not disappear or appear. 
The SoH defines in more detail, which changes for the clusters are stable and which changes indicate that the clusters are instable.

@@

The aggregation level is a slice plane through our three dimensional space. 
This is an example how the results can look with visualize representations of the calculated 
rasters and the raw data.
We evalute only the aggregation with fixed W and fixed F.
\begin{definition} Aggregation run:
\begin{displaymath}
\SOHUP( G^*(R_z, W, st, F), G^*(R_{z+1}, W, st, F) )
\end{displaymath}
\begin{displaymath}
\SOHDOWN( G^*(R_z, W, st, F), G^*(R_{z+1}, W, st, F) )
\end{displaymath}
\begin{displaymath}
z \in [1,6], dim(W)=11,dim(F)=41, G^* \in [Standard, Focal]
\end{displaymath}
\end{definition}

@@

\subsection{Blur}
We also made an example for the variation of the weight size.
Blur is a slice plane through our three dimensional space. 
W is changed from 7 to 29 with a stepsize of 2, F and the aggregation level is fixed.
\begin{definition} Blur run:
\begin{displaymath}
\SOHUP( G^*(R_z, W_i, st, F), G^*(R_{z}, W_{i+2}, st, F) )
\end{displaymath}
\begin{displaymath}
\SOHDOWN( G^*(R_z, W_i, st, F), G^*(R_{z}, W_{i+2}, st, F) )
\end{displaymath}
\begin{displaymath}
z =3, i \in [1,6],dim(F)=41, G^* \in [Standard, Focal]
\end{displaymath}
\end{definition}
The blur results are plotted in Fig.~\ref{fig:Blur}. We show how the weight matrix is increasing
and how $G^*$ and Focal $G^*$ changes bases on W.
The slice plane of the weight dimension is consistent with figure ~\ref{fig:SoHWeight}.
Higher weight leads in general to better results for Focal $G^*$. 
$G^*$ doesn't fit to the mean of our whiskerplot.

>>>>

Aggregation size 1 means we aggregate every point, which was in range of $100x100 \cdot 0.000001$ into one pixel. 
For aggregation size Z we aggregated ZxZ pixel from aggregated size 1 into a new pixel.
%
For our measurements we specified the following data series:
\begin{itemize}
 \item $W_i$: The weight matrix W is from 3 to 47 with a stepsize of 4.
 \item $F_j$: The focal matrix F is from  17 to 137 with a stepsize of 12. F is ignored for $G^*$ but not for Focal $G^*$
 \item $R_z$: The aggregation level is from 1 to 6 with a stepsize of 1. R represents the raster
\end{itemize}
\begin{definition}
The SoH for a singled evalution run in the weight dimension is defined as:
\begin{displaymath}
\SOHUP( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_z, W_{3+(i+1) \cdot 4}, st, F_{17+j \cdot 12}) ) 
\end{displaymath}
\begin{displaymath}
\SOHDOWN( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_z, W_{3+(i+1) \cdot 4}, st, F_{17+j \cdot 12}) )
\end{displaymath}
\begin{displaymath}
z \in [1,6], i,j \in [0,10], G^* \in [Standard, Focal]
\end{displaymath}
The SoH for a singled evalution run in the focal dimension is defined as:
\begin{displaymath}
\SOHUP( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_z, W_{3+i \cdot 4}, st, F_{17+(j+1) \cdot 12}) )
\end{displaymath}
\begin{displaymath}
\SOHDOWN( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_z, W_{3+i \cdot 4}, st, F_{17+(j+1) \cdot 12}) )
\end{displaymath}
\begin{displaymath}
z \in [1,6], i,j \in [0,10], G^* \in [Standard, Focal]
\end{displaymath}
The SoH for a singled evalution run in the aggregation dimension is defined as:
\begin{displaymath}
\SOHUP( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_{z+1}, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) )
\end{displaymath}
\begin{displaymath}
\SOHDOWN( G^*(R_z, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}), G^*(R_{z+1}, W_{3+i \cdot 4}, st, F_{17+j \cdot 12}) )
\end{displaymath}
\begin{displaymath}
z \in [1,6], i,j \in [0,10], G^* \in [Standard, Focal]
\end{displaymath}
\end{definition}

@@

\subsection{Clumping}
The SoH needs a parent and a child. Clusters can be calculated different. For $G^*$ a sigmoid can be used. Values above 2.58 and under -2.58 means in less then 
1\% of the cases you are wrong. The values of Focal $G^*$ depend on the focal size F. Therefore, we decide all values in the top quantile belong to a clusters.
For clustering we grouped the neighbourhood with values in the top quantile to one cluster. 
Neigbours are are pixels with touching edges which leads for every pixel to 8 neigbours.
The clustering can be expressed in R with clumping, TODO which package and parametrisations.
In Fig.~\ref{fig:Clumping} we visualized the clusters. The clusters are marked in different colours yellow (child) and violet (parent).
It can seen that the results from $G^*$ and Focal $G^*$ differ. Focal $G^*$ has more smaller clusters which are distributed over the complete raster.
Not overlapping clusters should be not stable because if we changed the parametrisation we want that the clusters do not disappear or appear. 
The SoH defines in more detail, which changes for the clusters are stable and which changes indicate that the clusters are instable.

@@

The aggregation level is a slice plane through our three dimensional space. 
This is an example how the results can look with visualize representations of the calculated 
rasters and the raw data.
We evalute only the aggregation with fixed W and fixed F. In contrast we included the negative clusters. They where exluded for our 3 dimensional space because
the water had to much influence.
\begin{definition} Aggregation run:
\begin{displaymath}
\SOHUP( G^*(R_z, W, st, F), G^*(R_{z+1}, W, st, F) )
\end{displaymath}
\begin{displaymath}
\SOHDOWN( G^*(R_z, W, st, F), G^*(R_{z+1}, W, st, F) )
\end{displaymath}
\begin{displaymath}
z \in [1,6], dim(W)=11,dim(F)=41, G^* \in [Standard, Focal]
\end{displaymath}
\end{definition}

@@

\subsection{Blur}
We also made an example for the variation of the weight size W.
Blur is a slice plane through our three dimensional space. 
W is changed from 7 to 29 with a stepsize of 2, F and the aggregation level is fixed.
For blur we also included the negative clusters which resulted in a surprising result.
\begin{definition} Blur run:
\begin{displaymath}
\SOHUP( G^*(R_z, W_{7+i}, st, F), G^*(R_{z}, W_{7+i+2}, st, F) )
\end{displaymath}
\begin{displaymath}
\SOHDOWN( G^*(R_z, W_{7+i}, st, F), G^*(R_{z}, W_{7+i+2}, st, F) )
\end{displaymath}
\begin{displaymath}
z =3, i \in [1,6],dim(F)=41, G^* \in [Standard, Focal]
\end{displaymath}
\end{definition}
The blur results are plotted in Fig.~\ref{fig:Blur}. The weight matrix is shown in the first row, with increasing size.
The scond and thrid row sho how $G^*$ and Focal $G^*$ changes based on W.
This example is a slice plane of the weight dimension ploted in figure ~\ref{fig:SoHWeight}.
It can be seen that increase of the weight size leads in general to better results for Focal $G^*$. 
$G^*$ compared to the mean of our whiskerplot does not fit in the picture because it leads to better results than $G^*$.
